\doublespacing
\chapter{Introduction}

%\version{v1.11.2015}
This is the first chapter of our project report. In this chapter we have describe what is the need that lead us to create the proposed web application. This chapter includes a brief introduction to problem statement, problem description, objectives and scope.

\section{Problem Statement}
Now a days, we are seeing the rapid growth in food wastage and at the same time we are seeing the shortage of the food globally \cite{wenlock1980household}. As per World Health Organization (WHO) the report one third of the food produced in the world is never consumed and it is being wasted or expired. On other hand most of the people face extreme shortage of food.  Some of the food problem that arises are the following:
\begin{enumerate}
    \item Food production companies (e.g. milk, bread) working on small or big scale faces the problem of expired food due to which they have to face huge losses.
    \item Marriage marquees, food chains, hotels also face problem of leftover food.
    \item Families in big cities faces the problem of kharat and donations.
\end{enumerate}
The population is increasing, and, in few years, there will be more food wasted. So, there is need to control these problems because it prevents both wastage of food and financial losses. All the above-mentioned problems will be solved through our web application.

	
\section{Objectives}
We are developing a web application for online service in which marquees, hotels, food chains (KFC, McDonald etc.) and food production companies can place bid for their leftover food and also food items near to the expiry dates make the publicly available for NGOs, orphan houses, Old age homes, Madrases and even local houses at half and lowest prices possible.
\section{Project Scope}
The proposed system will assist the food production companies in finding the clients for their products which are near to expire. It will also assist the people who can help needy people with food. The donator can place a bid on the products to make them available for interested buyers. Many food donators will be attracted using our web application. The unregistered person can also register with our website. All the information regarding the bidding will be displayed to him, if he wants to bid then he must login.
\section{Approach}
With the help of the our web Application, the food donators and companies will be able to find the Nearest buyers just before their products expiry dates. As today the world is evolving toward digitalization and in Pakistan when food is near to expiry date finding the buyer of that products is almost impossible and then we have to waste it and the needy people has to suffer.
\section{Problem Description}
Food is amount the most important source of energy for us humans. One side of country we see people suffering for the shortage of the food and the other side we see lot of food is being wasted in our country. This can be reduced just by giving right to right people at right time. The food companies produces food items that has the expiry dates. When the products are expires, They have no option but to waste it. The same problems are with marriage marquees and hotels they also have to waste the excess food. On other hand we face the shortage of the food in our country. The people in big cities also face problems of kharat and food donations.